More than one Author with different Affiliations

### 2016-01-13 manuscript.tex
add small results paragraph
results

A number of tools have recently been published to handle high throughput sequencing data \citep{garrigan2013popbam, purcell2007plink, danecek2011variant, hutter2006genome}, but the majority of these either make limiting assumptions about the data (e.g., all sites have been sequenced, all genomes are haploid, sequencing is to sufficient depth, all individuals are outcrossing) or are specialized tools offering a narrow set of analysis options. 
Korneliussen et al. \citep{korneliussen2014angsd} recently published the software package ANGSD, which enables users to flexibly perform a large number of common population genetic analyses, including diversity statistics, Patterson's D-statistic test of admixture \citep{Durand:2011jd}, site frequency spectrum estimation \citep{pmid22911679}, and neutrality test statistics \citep{korneliussen_calculation_2013}.
One of the most important features of ANGSD is that most analyses are performed directly on genotype likelihoods, freeing users from the requirement of calling variants or genotypes and permitting analysis of low-coverage data or sequences with large amounts of missing data.

@@

\begin{table}
\begin{center}
    \begin{tabular}{ | l | p{5cm} |}
    \hline
    Methods Implemented & Interactive Graphing \\ \hline
    ABBA BABA & Yes \\ \hline
    Admixture & Yes  \\ \hline
    Ancestral Sequence & N/A \\ \hline
    Genotype Likelihoods & N/A \\ \hline
    Inbreeding Coefficients & N/A \\ \hline
    PCA & Yes \\ \hline
    Site Frequency Spectrum & Yes \\ \hline
    Theta Calculation & Yes \\ \hline
    \end{tabular}
    \caption{Table of methods implemented in ANGSD-wrapper}
    \label{tab:methods}
    \end{center}
\end{table}

@@

In order to use the plotting software, the user navigates to the desired tab and uploads the appropriate file of results. 
The Shiny server automatically parses ANGSD output files and creates the resulting plot(s) (Figure \ref{fig:theta}), which can be saved using the browser's built in image saving capabilities.

@@

\section*{Results}

\begin{figure}
\centering
\includegraphics[width=\linewidth]{figures/MainTextWorkflow.pdf}
\caption{Example analysis workflow diagram.}
\label{fig:workflow}
\end{figure}

@@

\section*{Discussion}

@@

\section*{Acknowledgements}
We acknowledge funding support from the US National Science Foundation (IOS-1238014 to JRI and IOS-1339393 to PLM) and funding from the UC Davis Plant Sciences Department.  We thank members of the Ross-Ibarra and Morrell labs for discussion and software testing. We thank the authors of ANGSD and related programs for answering questions, particularly Matteo Fumagalli and Filipe Vieira. Finally, we would like to thank Felix Andrews for statistical advice, although we did not follow it.

\bibliographystyle{unsrt}
\bibliography{references}

>>>>

A number of tools have recently been published to handle high throughput sequencing data \citep{garrigan2013popbam, purcell2007plink, danecek2011variant, hutter2006genome}, but the majority of these either make limiting assumptions about the data (e.g., all sites have been sequenced, all genomes are haploid, sequencing is to sufficient depth, all individuals are outcrossing) or are specialized tools offering a narrow set of analysis options. 
Korneliussen et al. \citep{korneliussen2014angsd} recently published the software package ANGSD, which enables users to flexibly perform a large number of common population genetic analyses, including diversity statistics, admixture analysis including Patterson's D statistic \citep{Durand:2011jd}, site frequency spectrum estimation \citep{pmid22911679}, and neutrality test statistics \citep{korneliussen_calculation_2013}.\jri{are all these within ANGSD or are some ngsPopgen?}
One of the most important features of ANGSD is that most analyses are performed directly on genotype likelihoods, freeing users from the requirement of calling variants or genotypes and permitting analysis of low-coverage data or sequences with large amounts of missing data.

@@

\begin{table}
\begin{center}
    \begin{tabular}{ | l | p{5cm} |}
    \hline
    \textbf{Methods Implemented} & \textbf{Interactive Graphing} \\ \hline \hline
    Patterson's D (ABBA-BABA) & Yes \\ \hline
    Admixture & Yes  \\ \hline
    Ancestral Sequence & No \\ \hline
    Genotype Likelihoods & No \\ \hline
    Inbreeding Coefficients & No \\ \hline
    PCA & Yes \\ \hline
    Site Frequency Spectrum & Yes \\ \hline
    Diversity Statistics  & Yes \\ \hline
    \end{tabular}
    \caption{Table of methods implemented in ANGSD-wrapper}
    \label{tab:methods}
    \end{center}
\end{table}
\jri{list diversity statistics in parentheses. what about Fst?}

@@

In order to use the plotting software, the user navigates to the desired tab and uploads the appropriate file of results. 
The Shiny server automatically parses ANGSD output files and creates the resulting plot(s) (Figure \ref{fig:theta}), which can be saved using the browser's built in image saving capabilities. \jri{add genes from gff. i don't think it's Mb 1-10, pls check. if so, is x-axis wrong?}

@@

\section*{Example data}
\jri{show k=2 and k=3 for adxmxture in supp.}
\begin{figure}
\centering
\includegraphics[width=\linewidth]{figures/MainTextWorkflow.pdf}
\caption{Example analysis workflow diagram.}
\label{fig:workflow}
\end{figure}

@@

As a demonstration of analyses in ANGSD-wrapper, we explore patterns of diversity in a single genomic region of a subset of domesticated maize and wild teosinte. We used resequenced samples from the HapMap2 project  and calculated summary statistics using a 10 megabase region on chromosome 10.\jri{cite Chia 2012 instead. include region \& mean depth, supp. table w/ sample names \& depth. include download link.}

We first use \X\ to estimate the site frequency spectrum (SFS) of both maize and its wild progenitor \texit{Zea mays} ssp. \textit{parviglumis}, assuming an inbreeding coefficient of $F=1$ since these are all highly inbred samples. 
Consistent with previous results \citep{hufford2012comparative}, we show that the maize SFS is skewed towards more intermediate-frequency variants (Figure \ref{fig:figure3}A-B), likely a result of the bottleneck associated with maize domestication.\jri{cite Tim} 
We find further evidence of the effect of domestication using \X, revealing lower levels overall levels of diversity in maize (Figure \ref{fig:figure3}C).\jri{fill in \X's with which A-W script we used. probably need to modify this to mention Tripsacum and generation of the ancestral seq. and which A-W script we used for that.}
Using \X, we then scan our example region for windows with elevated differentiation between maize and teosinte. 
The mean $F_{ST}$ in this region is \X, close to the genome-wide reported value of \X \citep{hufford2012comparative} .  
The \X windows in the 1\% tail of highest $F_{ST}$ values include genes several genes identified as potential targets of selection during domestication in \citep{hufford2012comparative}

We next include two samples of the related wild teosinte \textit{Zea mays} ssp. {mexicana} to assess evidence for admixture.  
Figure \ref{fig:admixture}) identifies previously unreported structure within the domesticated maize samples used in \citep{hufford2012comparative}

@@

\section*{Acknowledgements}
We acknowledge funding support from the US National Science Foundation (IOS-1238014 to JRI and IOS-1339393 to PLM) and funding from the UC Davis Plant Sciences Department.  We thank members of the Ross-Ibarra and Morrell labs for discussion and software testing. We thank the authors of ANGSD and related programs for answering questions, particularly Matteo Fumagalli and Filipe Vieira. Finally, we would like to thank Felix Andrews for statistical advice, although we did not follow it. 
\jri{make sure figures/tables go where Mol. Ecol. Res. suggests (at end? in text?)}
\clearpage
\bibliographystyle{unsrt}
\bibliography{references}
